---
title: "AfricanRegions"
author: "Armand Bester"
date: "22 November 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


<br>

#### On behalve of the authors of the work:
### Application of sero-epidemiology data to informing interventions for HBV in Africa: should diagnosis and treatment replace catch-up vaccination?

<br>


#### Load some handy libraries
```{r libs}
library(readxl)
library(dplyr)
library(ggplot2)
library(leaflet)
library(readr)
library(ggmap)
library(maptools)
library(rgeos)
library(scales)
library(RColorBrewer)
library(gpclib)
library(gridExtra)
library(viridis)
library(ggforce)

```

<br>

#### Load the data and select the columns needed.

From the data it seems the grey rows are to be added or there is no data yet.  I removed the rows where Citation is blank/NA

```{r getData}
# ox.df <- read_xlsx('180907 Metadata for Prisma analysis REVIEWED.xlsx', col_names = TRUE, range = "A1:S121")
# # remove all the rows where citation is NA
# ox.df <- ox.df %>%
#   filter(!is.na(ox.df$Citation))



ox.df <- read_delim("AfricaHBV_update.csv", delim = '|', col_names = TRUE, 
                    col_types = "cccccccccddcddcdddcdddcdd")

ox.df <- ox.df %>%
   filter(!is.na(ox.df$Citation))

head(ox.df)
str(ox.df)


#country_location <- ox.df %>% 
#  select(c('Country','Location'))
  
#country_location <- country_location[!duplicated(country_location[c(1,2)]), ]
#write_delim(country_location, 'GeoCoding/places.csv')
```

Make the column names a little bit more R friendly





#### Read in the coordinates


```{r coords}
coords.df <- read_delim("GeoCoding/placesWithlocs.csv", delim = "|", col_names = FALSE)

colnames(coords.df) <- c("lat", "long", "Place")

```

<br>

#### Merge the coordinates with the data

<br>

```{r merge}


tmp.ox.df <- ox.df
tmp.ox.df$Place <- paste0(tmp.ox.df$Country, " ", tmp.ox.df$Location)
tmp.ox.df$Place <- gsub( " NA", "", tmp.ox.df$Place)


ox.df <- merge(tmp.ox.df, coords.df, by = "Place")

tmp.ox.df[tmp.ox.df$Place %in% ox.df$Place == FALSE, ]


rm(tmp.ox.df)
```


<br>

#### Plotting

<br>

```{r createFigs, fig.width=7, fig.height=7}

# read in the shape file
africa.shp <- readShapeSpatial("Africa_SHP/Africa.shp")

# permit the use for gpclib
gpclibPermit()

# convert the shape file to a dataframe
africa.shp.f <- fortify(africa.shp, region = "COUNTRY")

# correctly order the polygon data
africa.plot<-africa.shp.f[order(africa.shp.f$order), ] 

# plot
fig1A <- ggplot()+
  geom_polygon(data = africa.plot,
               aes(x = long, y = lat, group = group),
               color = "black", size = 0.2, fill = "grey")+
  coord_map()+
  geom_circle(data = ox.df, aes(x0 = long, y0 = lat, 
                                color = ox.df$HbsAg_prevalence, #HBsAgPrevalence, 
                                r = log10(ox.df$Size_of_cohort),
                                fill = ox.df$HbsAg_prevalence), alpha = 0.3)+
  scale_color_viridis(name = "", direction = -1)+
  scale_fill_viridis(name = "", direction = -1)+
  theme(panel.background = element_blank(), axis.text = element_blank(),
        axis.title = element_blank(), axis.ticks = element_blank())+
  ggtitle("A") + theme(plot.title = element_text(size = 30), legend.text = element_text(size = 20))

fig1A



fig1B <- ggplot()+
  geom_polygon(data = africa.plot,
               aes(x = long, y = lat, group = group),
               color = "black", size = 0.2, fill = "grey")+
  coord_map()+
  geom_circle(data = ox.df, aes(x0 = long, y0 = lat, 
                                color = ox.df$`Anti-Hbc_prevalence`, #`Anti-HBc_only_prevalence`, 
                                r = log10(ox.df$Size_of_cohort_ext),
                                fill = ox.df$`Anti-Hbc_prevalence`), alpha = 0.3)+
  scale_color_viridis(name = "", direction = -1)+
  scale_fill_viridis(name = "", direction = -1)+
  theme(panel.background = element_blank(), axis.text = element_blank(),
        axis.title = element_blank(), axis.ticks = element_blank())+
  ggtitle("B") + theme(plot.title = element_text(size = 30), legend.text = element_text(size = 20))

fig1B

fig1C <- ggplot()+
  geom_polygon(data = africa.plot,
               aes(x = long, y = lat, group = group),
               color = "black", size = 0.2, fill = "grey")+
  coord_map()+
  geom_circle(data = ox.df, aes(x0 = long, y0 = lat, 
                                color = ox.df$Estimated_susceptible_population/100, # To keep consistently have variables as ratios
                                r = log10(ox.df$Size_of_cohort),
                                fill = ox.df$Estimated_susceptible_population/100), alpha = 0.3)+
  scale_color_viridis(name = "", direction = -1)+
  scale_fill_viridis(name = "", direction = -1)+
  theme(panel.background = element_blank(), axis.text = element_blank(),
        axis.title = element_blank(), axis.ticks = element_blank())+
  ggtitle("C") + theme(plot.title = element_text(size = 30), legend.text = element_text(size = 20))


fig1C

```


<br>
#### Final figure
<br>

```{r}

# save the figures seperately and use Inkscape to create the final image
ggsave("fig1A.jpeg", fig1A, dpi = 600, width = 7, height = 7)
ggsave("fig1B.jpeg", fig1B, dpi = 600, width = 7, height = 7)
ggsave("fig1C.jpeg", fig1C, dpi = 600, width = 7, height = 7)



```


<br>
<br>
<br>
<br>
























