---
title: "AfricanRegions"
author: "Armand Bester"
date: "11 September 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


<br>

#### On behalve of the authors of the work:
### Application of sero-epidemiology data to informing interventions for HBV in Africa: should diagnosis and treatment replace catch-up vaccination?

<br>


#### Load some handy libraries
```{r libs}
library(readxl)
library(dplyr)
library(ggplot2)
library(leaflet)
library(readr)
library(ggmap)
library(maptools)
library(rgeos)
library(scales)
library(RColorBrewer)
library(gpclib)
library(gridExtra)


```

<br>

#### Load the data and select the columns needed.

From the data it seems the grey rows are to be added or there is no data yet.  I removed the rows where Citation is blank/NA

```{r getData}
# ox.df <- read_xlsx('180907 Metadata for Prisma analysis REVIEWED.xlsx', col_names = TRUE, range = "A1:S121") 
# # remove all the rows where citation is NA
# ox.df <- ox.df %>%
#   filter(!is.na(ox.df$Citation))


ox.df <- read_csv("AfricaHBV.csv", col_names = TRUE)
```


#### Average the 5 regions and place it in a data frame

<br>

Average Anit-HBc only

<br>

```{r AvgAntiHbcOnly}

### Do some ground work
# convert cohort size to numeric
ox.df$CohortSize <- as.numeric(ox.df$CohortSize)
ox.df$`Anti-HBc_only_prevalence ` <- as.numeric(ox.df$`Anti-HBc_only_prevalence`)

AntiHBcOnly <- ox.df %>% 
 group_by(AfricanRegion) %>% 
  summarise(mean = mean(`Anti-HBc_only_prevalence`), n = n())

colnames(AntiHBcOnly) <- c("region", "AntiHBcOnly", "n")

```

<br>

Average the anti-HBc prevelance 

<br>

```{r AvgAntiHbc}

AntiHBc <- ox.df %>% 
 group_by(AfricanRegion) %>% 
  summarise(mean = mean(`Anti-HbcPrevalence`), n = n())

colnames(AntiHBc) <- c("region", "AntiHBc", "n")

```

<br>

Average the Estimated suseptable population size

<br>

```{r EstSusPop}

EstSusPop <- ox.df %>% 
 group_by(AfricanRegion) %>% 
  summarise(mean = mean(EstimatedSusceptiblePopulation), n = n())

colnames(EstSusPop) <- c("region", "EstSusPop", "n")

```

<br>

Average the SAg prevelance

<br>

```{r SAgPrev}

HBsAgPrevalence <- ox.df %>% 
 group_by(AfricanRegion) %>% 
  summarise(mean = mean(HBsAgPrevalence), n = n())

colnames(HBsAgPrevalence) <- c("region", "HBsAgPrevalence", "n")


```

<br>

#### Combine the prevelance data by region into one convenient dataframe

<br>

```{r combine}

plot.df <- cbind(AntiHBc[,c(1,2)], AntiHBcOnly[,2], 
                 EstSusPop[,2], HBsAgPrevalence[,c(2,3)])

# clean up a bit
rm(AntiHBc, AntiHBcOnly, HBsAgPrevalence, EstSusPop)

```

<br>

#### Create coutry/region lookup table from Anna's data

<br>

```{r countryRegionTable}

region.lookup.df <- read_xlsx('180907 Metadata for Prisma analysis REVIEWED.xlsx', 
                              col_names = TRUE, range = "A1:R121") 

region.lookup.df <- region.lookup.df %>% 
  select(c(1,16))

# Due to small differances in the country names, add the 'alternative' spelling to the lookup table
add.df <- data.frame("id" = c("Cote d`Ivoire", "Congo-Brazzaville", "Swaziland"), 
                     "region" = c("West", "Central", "South"))

colnames(region.lookup.df) <- c("id", "region")

region.lookup.df <- rbind(region.lookup.df, add.df)

table(region.lookup.df$region)

rm(add.df) # we don't need this anymore
```


<br>

#### Plotting

<br>

```{r}

# read in the shape file
africa.shp <- readShapeSpatial("Africa_SHP/Africa.shp")

# permit the use for gpclib
gpclibPermit()

# convert the shape file to a dataframe
africa.shp.f <- fortify(africa.shp, region = "COUNTRY")

# merge regional data
merge.shp.coef<-merge(africa.shp.f, region.lookup.df, by="id", all.x=TRUE)

# merge prevelance data
merge.shp.coef <- merge(merge.shp.coef, plot.df, by = "region", all.x=TRUE)

# correctly order the polygon data
final.plot<-merge.shp.coef[order(merge.shp.coef$order), ] 

# plot
fig1G <- ggplot()+
  geom_polygon(data = final.plot,
               aes(x = long, y = lat, group = group, fill = final.plot$HBsAgPrevalence),
               color = "black", size = 0.2)+
  coord_map()+
  scale_fill_distiller(palette = "Greens", direction = 1, name = "")+
  theme(panel.background = element_blank(), axis.text = element_blank(),
        axis.title = element_blank(), axis.ticks = element_blank())+
  ggtitle("G") + theme(plot.title = element_text(size = 30), legend.text = element_text(size = 20))

# plot
fig1H <- ggplot()+
  geom_polygon(data = final.plot,
               aes(x = long, y = lat, group = group, fill = final.plot$AntiHBc),
               color = "black", size = 0.2)+
  coord_map()+
  scale_fill_distiller(palette = "Greens", direction = 1, name = "")+
  theme(panel.background = element_blank(), axis.text = element_blank(),
        axis.title = element_blank(), axis.ticks = element_blank())+
  ggtitle("H") + theme(plot.title = element_text(size = 30), legend.text = element_text(size = 20))

# plot
fig1I <- ggplot()+
  geom_polygon(data = final.plot,
               aes(x = long, y = lat, group = group, fill = final.plot$EstSusPop),
               color = "black", size = 0.2)+
  coord_map()+
  scale_fill_distiller(palette = "Greens", direction = 1, name = "")+
  theme(panel.background = element_blank(), axis.text = element_blank(),
        axis.title = element_blank(), axis.ticks = element_blank())+
  ggtitle("I") + theme(plot.title = element_text(size = 30), legend.text = element_text(size = 20))



# resources for geoplotting

# http://www.maplibrary.org/library/stacks/Africa/index.htm
# http://rforpublichealth.blogspot.com/2015/10/mapping-with-ggplot-create-nice.html

```

<br>
#### Final figure
<br>

```{r}

# plots = list(fig1G,
#              fig1H,
#              fig1I)
#              
# figure <- grid.arrange(grobs= lapply(plots, "+", theme(plot.margin=margin(1,1,1,1))), 
#                        ncol = 3, nrow = 1)
# 
# figure <- grid.arrange(arrangeGrob(fig1G, fig1H, fig1I, ncol = 3))
# 
# figure

# save the figures seperately and use Inkscape to create the final image
ggsave("fig1G.jpeg", fig1G, dpi = 600, height = 7, width = 7)
ggsave("fig1H.jpeg", fig1H, dpi = 600, height = 7, width = 7)
ggsave("fig1I.jpeg", fig1I, dpi = 600, height = 7, width = 7)



```


<br>
<br>
<br>
<br>
























