---
title: "AfricanRegions"
author: "Armand Bester"
date: "11 September 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


<br>

#### On behalve of the authors of the work:
### Application of sero-epidemiology data to informing interventions for HBV in Africa: should diagnosis and treatment replace catch-up vaccination?

<br>


#### Load some handy libraries
```{r libs}
library(readxl)
library(dplyr)
library(ggplot2)
library(leaflet)
library(readr)
library(ggmap)
library(maptools)
library(rgeos)
library(scales)
library(RColorBrewer)
library(gpclib)
library(gridExtra)
library(viridis)
library(ggforce)

```

<br>

#### Load the data and select the columns needed.

From the data it seems the grey rows are to be added or there is no data yet.  I removed the rows where Citation is blank/NA

```{r getData}
# ox.df <- read_xlsx('180907 Metadata for Prisma analysis REVIEWED.xlsx', col_names = TRUE, range = "A1:S121")
# # remove all the rows where citation is NA
# ox.df <- ox.df %>%
#   filter(!is.na(ox.df$Citation))



ox.df <- read_csv("AfricaHBV.csv", col_names = TRUE)

```

Make the column names a little bit more R friendly


```{r colnames}

colnames(ox.df) <- c("Country", "Continent_Island", "Citation", "PMID_DOI","YearPublished", "SamplingDate", "Location", 
                     "CohortCharacteristics", "CohortSize","CohortSizeAntiHBc", "Age", "Anti-HbcPrevalence_perc", 
                     "Anti-HBc_only_prevalence", "HBsAgPrevalence_perc", "EstimatedSusceptiblePopulation", "AfricanRegion", 
                     "Anti-HbcPrevalence", "HBsAgPrevalence", "Anti-HBc_HBsAg_ratio")
# write_csv(ox.df, "AfricaHBV.csv")
```


#### Read in the coordinates


```{r coords}
coords.df <- read_delim("GeoCoding/placesWithlocs.csv", delim = "|", col_names = FALSE)

colnames(coords.df) <- c("lat", "long", "Place")

# read in the places and simplified places form the geocoding folder
places.df <- read_csv("GeoCoding/places.csv") %>% 
  select(c(4,5))

# merge the coordinates with the places df

places.df <- merge(places.df, coords.df, by = "Place")

rm(coords.df)
```

<br>

#### Merge the coordinates with the data

<br>

```{r merge}
tmp.ox.df <- ox.df
tmp.ox.df$Place <- paste0(tmp.ox.df$Country, ", ", tmp.ox.df$Location)

ox.df <- merge(tmp.ox.df, places.df, by = "Place") %>% 
  select(-c(13,15))


rm(tmp.ox.df)
```


<br>

#### Plotting

<br>

```{r createFigs, fig.width=7, fig.height=7}

# create a color palette
# pal <- colorNumeric(
#     palette = "viridis",
#     domain = ox.df$HBsAgPrevalence
#   )

# read in the shape file
africa.shp <- readShapeSpatial("Africa_SHP/Africa.shp")

# permit the use for gpclib
gpclibPermit()

# convert the shape file to a dataframe
africa.shp.f <- fortify(africa.shp, region = "COUNTRY")

# correctly order the polygon data
africa.plot<-africa.shp.f[order(africa.shp.f$order), ] 

# plot
fig1A <- ggplot()+
  geom_polygon(data = africa.plot,
               aes(x = long, y = lat, group = group),
               color = "black", size = 0.2, fill = "grey")+
  coord_map()+
  geom_circle(data = ox.df, aes(x0 = long, y0 = lat, 
                                color = ox.df$HBsAgPrevalence, 
                                r = log10(ox.df$CohortSize),
                                fill = ox.df$HBsAgPrevalence), alpha = 0.3)+
  scale_color_viridis(name = "", direction = -1)+
  scale_fill_viridis(name = "", direction = -1)+
  theme(panel.background = element_blank(), axis.text = element_blank(),
        axis.title = element_blank(), axis.ticks = element_blank())+
  ggtitle("A") + theme(plot.title = element_text(size = 30), legend.text = element_text(size = 20))

fig1A



fig1B <- ggplot()+
  geom_polygon(data = africa.plot,
               aes(x = long, y = lat, group = group),
               color = "black", size = 0.2, fill = "grey")+
  coord_map()+
  geom_circle(data = ox.df, aes(x0 = long, y0 = lat, 
                                color = ox.df$`Anti-HBc_only_prevalence`, 
                                r = log10(ox.df$CohortSizeAntiHBc),
                                fill = ox.df$`Anti-HBc_only_prevalence`), alpha = 0.3)+
  scale_color_viridis(name = "", direction = -1)+
  scale_fill_viridis(name = "", direction = -1)+
  theme(panel.background = element_blank(), axis.text = element_blank(),
        axis.title = element_blank(), axis.ticks = element_blank())+
  ggtitle("B") + theme(plot.title = element_text(size = 30), legend.text = element_text(size = 20))


fig1C <- ggplot()+
  geom_polygon(data = africa.plot,
               aes(x = long, y = lat, group = group),
               color = "black", size = 0.2, fill = "grey")+
  coord_map()+
  geom_circle(data = ox.df, aes(x0 = long, y0 = lat, 
                                color = ox.df$EstimatedSusceptiblePopulation, 
                                r = log10(ox.df$CohortSizeAntiHBc),
                                fill = ox.df$EstimatedSusceptiblePopulation), alpha = 0.3)+
  scale_color_viridis(name = "", direction = -1)+
  scale_fill_viridis(name = "", direction = -1)+
  theme(panel.background = element_blank(), axis.text = element_blank(),
        axis.title = element_blank(), axis.ticks = element_blank())+
  ggtitle("C") + theme(plot.title = element_text(size = 30), legend.text = element_text(size = 20))




```


<br>
#### Final figure
<br>

```{r}

# plots = list(fig1G,
#              fig1H,
#              fig1I)
#              
# figure <- grid.arrange(grobs= lapply(plots, "+", theme(plot.margin=margin(1,1,1,1))), 
#                        ncol = 3, nrow = 1)
# 
# figure <- grid.arrange(arrangeGrob(fig1G, fig1H, fig1I, ncol = 3))
# 
# figure

# save the figures seperately and use Inkscape to create the final image
ggsave("fig1A.jpeg", fig1A, dpi = 600, width = 7, height = 7)
ggsave("fig1B.jpeg", fig1B, dpi = 600, width = 7, height = 7)
ggsave("fig1C.jpeg", fig1C, dpi = 600, width = 7, height = 7)



```


<br>
<br>
<br>
<br>
























